% !TEX root = ../main.tex

% open questions section

\section{Open questions and research directions}

\subsection{Open questions}

In 2000, Talagrand \cite*{talagrand:1995} proposed more inequalities in dertermining bounds. 
Generally he extends the Bounded Differences Inequality to further applicable fields. 
For example, he extends it towards the form of integration. 
Besides, he also discusses the optimization (or sharpening) on the bounds based on different objects.
Can we develop further specific inequalities for more narrowed objects? 
In other words, for some specific application and problems, can we simplify the Bounded Differences Inequality for more precise using?
Also, can we use the original Bounded Differences Inequality to proof other concept? 

For example the "Hamming Distance": \cite*{hmaji:2017}

Let $x, x' \in \Omega:= \Omega_1 \times \dots \Omega_n$. We define
    \begin{equation}
        d_{H}\left(x, x^{\prime}\right):=\left|\left\{i: x_{i} \neq x_{i}^{\prime}\right\}\right|
    \end{equation}

and define the set $A_k := \{ x: x \in \Omega, d_H (x,A) \leq k\}$


Can we prove that 
\begin{equation}
    P[X \in A] \cdot P\left[d_{H}(X, A) \geqslant t\right] \leqslant \exp \left(-t^{2} / 2 n\right)
\end{equation}

\subsection{Doob construction}
A Doob martingale is a construction of a stochastic process to approximates a given random variable.
It has the properties of the martingale with respect to the given filtration. 

The Doob construction can be used to help prove the Bounded Differences Inequality by following brief steps. \cite*{Bartlett:2020}

\begin{equation}
    \begin{aligned}
    Y_{i} &=\mathbb{E}\left[f(X) \mid X_{1}^{i}\right] \\
    D_{i} &=Y_{i}-Y_{i-1} \\
    f(X)-\mathbb{E} f(X) &=\sum_{i=1}^{n} D_{i}
    \end{aligned}
\end{equation}
  
Then
\begin{equation}
    \begin{aligned}
    D_{i} &=Y_{i}-Y_{i-1}=\mathbb{E}\left[f(X) \mid X_{1}^{i}\right]-\mathbb{E}\left[f(X) \mid X_{1}^{i-1}\right] \\
    &=\mathbb{E}\left[\mathbb{E}\left[f(X) \mid X_{1}^{i}\right]-f(X) \mid X_{1}^{i-1}\right]
    \end{aligned}
\end{equation}
Thus $D_i$ is a random variable that falls in an interval of length no more than $B_i$.

Similarly, can we use the Doob construction in proof of extended bounded differences inequalities? 
For example, the inequalities proposed by Talagrand in 2020.